---
title: "Supplementary Figures"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{graphicx}
- \setkeys{Gin}{width=0.9\linewidth,keepaspectratio}  # 🔥 This forces figures to max 90% of the text width
- \usepackage{pdflscape}    
output:
  pdf_document: null
  latex_engine: pdflatex
  html_document:
    df_print: paged
---


\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 1
```

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
# knitr::include_graphics("fig/FigureS1_ill2.pdf"); i = i + 1
```

**Fig. S`r i`** | *tbd* Map of 35 islands surveyed by CREP across the tropical Pacific.
\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME.pdf"); i = i + 1
```
**Fig. S`r i`** | Seasonal variation in IME strength at each island complex. Lines are mean-monthly chl-a enhancement from January to December, ordered and coloured by island group.
\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME_pred.pdf"); i = i + 1
```
**Fig. S`r i`** | Spatial effects on chl-a enhancement for geomorphic features (top) and average oceanographic conditions (bottom) Lines are median posterior predictions (± 95% certainty intervals). Note different y-axis values between static and dynamic covariates.
\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME_seasonal_pred.pdf"); i = i + 1
```
**Fig. S`r i`** | Heatmap of seasonal effects on chl-a enhancement for a mixed layer depth, b precipitation and c both covariates combined. Islands with less than 1 mm monthly rainfall are shown in grey. All values are median posterior predictions excluding effects of other covariates.
\newpage

```{r, out.height="80%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_metab.pdf"); i = i + 1
```
**Fig. S`r i`** | Metabolic rate of reef-associated planktivores on coral reefs at 39 Pacific islands and atolls. Each point is a site-year combination (n = XX). 
\newpage