---
title: "Supplementary Figures"
header-includes:
  - \usepackage{pdflscape}
  - \usepackage{afterpage}
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: true
---


\newpage
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

```{r, echo=F} 
## set up figcounter
i = 1
```

```{r, out.width = "95%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
# knitr::include_graphics("fig/FigureS1_ill2.pdf"); i = i + 1
```

**Fig. S`r i`** | *tbd* Map of 35 islands surveyed by CREP across the tropical Pacific.

\begin{landscape}

```{r,out.width = "75%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME.pdf"); i = i + 1
```
\textbf{Fig. S`r i`} | Seasonal variation in IME strength at each island. Lines are mean-monthly chl-a enhancement from January to December, ordered and coloured by island group.
\end{landscape}
\newpage

```{r, out.width = "85%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME_pred.pdf"); i = i + 1
```
**Fig. S`r i`** | Spatial effects on chl-a enhancement for geomorphic features (top) and average oceanographic conditions (bottom) Lines are median posterior predictions (± 95% certainty intervals). Note different y-axis values between static and dynamic covariates.
\newpage

```{r, out.width = "85%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME_seasonal_pred.pdf"); i = i + 1
```
**Fig. S`r i`** | Heatmap of seasonal effects on chl-a enhancement for a mixed layer depth, b precipitation and c both covariates combined. Islands with less than 1 mm monthly rainfall are shown in grey. All values are median posterior predictions excluding effects of other covariates.
\newpage
\begin{landscape}

```{r, out.width = "95%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_MLD_amp.pdf"); i = i + 1
```
\textbf{Fig. S`r i`} | Seasonal variability in the mixed layer depth at each island. In a, lines are predicted mixed layer depth at each island from a General Additive Model with smoothers for time and month (cyclic), overlaid with points indicating timing of coral reef fish surveys.
\end{landscape}
\newpage


```{r, out.height="80%",out.width = "95%",  echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_metab.pdf"); i = i + 1
```
**Fig. S`r i`** | Respiration rate of reef-associated planktivores on coral reefs at 34 Pacific islands and atolls. Each point is the median respiration at each island, with jitter showing unique sites (n = 3,622). 
\newpage
\begin{landscape}

```{r, out.height="80%",out.width = "95%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_planktivore_time.pdf"); i = i + 1
```

\textbf{Fig. S`r i`} | Effect of survey year on planktivore respiration rate. Points are posterior medians with 95\% certainty intervals, coloured when the posterior did not overlap zero (red = negative, blue = positive).
\newpage

```{r, out.width = "95%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_herbivore_time.pdf"); i = i + 1
```

\textbf{Fig. S`r i`} | Effect of survey year on herbivore respiration rate. Points are posterior medians with 95\% certainty intervals, coloured when the posterior did not overlap zero (red = negative, blue = positive).
\newpage
\end{landscape}

```{r, out.height = "85%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_MLD_time_obs.pdf"); i = i + 1
```

**Fig. S`r i`** | Island-level temporal trends in the mixed layer depth layer from 1993-2026. a) is the observed mixed layer accounting for monthly variability and b)  occurrence of anomalously shallow (< 20 m than monthly mean, blue) or deep (>20 m than monthly mean, red) mixed layers. In a), lines are mean predicted mixed layer from generalised additive model, for each region (black with 95% CI filled by region), overlaid with mean island predictions (coloured lines). In b), lines are posterior median predictions with 95% and 50% certainty intervals.

```{r, out.width = "85%", echo=F,fig.align='center', warning=FALSE, message=FALSE}
knitr::include_graphics("fig/FigureSX_IME_time_covariates.pdf"); i = i + 1
```

**Fig. S`r i`** | Effects of mixed layer depth covariates on IME dynamics from 1997-2025. a) Probability of detecting an IME and b) IME strength (%). Lines are median posterior estimates with 95% and 50% certainty intervals.
